Hydras \& Co.

### 2022-05-14 doc/hydra-chapter.tex
deprecate 'battle' -> 'rounds'

% \begin{remark}
%  The class \texttt{free} is strongly related with the transitive closure  \texttt{round\_plus}, as expressed by the following lemmas.

% \vspace{4pt}
% \emph{From Module~\href{../theories/html/hydras.Hydra.Hydra_Lemmas.html}{Hydra.Hydra\_Lemmas}}

%  \begin{Coqsrc}
%  Lemma battle_free_equiv1 : forall i j h h',  
%              battle free i h j h' ->   h -+-> h'.

%  Lemma battle_free_equiv2 : forall h h',
%      h -+-> h' ->
%     forall i, exists j,  battle free i h j h'.
%  \end{Coqsrc}

% \end{remark}

@@

The following lemma  is a formal description of these first rounds, in terms of the
\texttt{battle} predicate.

@@

The following function returns the next configuration of the game.
Note that this function is defined only for making experiments and is not  ``certified''.  Formal proofs about our battle only start with the lemma
\texttt{step\_battle}, page~\pageref{lemma:step-battle}.

>>>>

@@

The following lemma  is a formal description of these first rounds, in terms of the \texttt{rounds} predicate.

@@

The following function returns the next configuration of the game.
Note that this function is defined only for making experiments and is not  ``certified''.  Formal proofs about our battle only start with the lemma
\texttt{step\_rounds}, page~\pageref{lemma:step-battle}.
